\documentclass[abstract=on]{scrreprt}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{blindtext}
\usepackage[utf8]{inputenc}
\usepackage{siunitx} %For unit handling%
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}}
\usepackage{amssymb, amsmath, cancel, ulem, graphicx, float, tabularx, multirow, bm}
\usepackage{amsmath}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

\author{Urs Gerber\\09-921-156 \and Gian-Luca Mateo\\11-113-545}
\date{7th of March 2013}

\title{Transverse oscillation of a string}
\subtitle{Practical course report}

\begin{document}

\maketitle

\tableofcontents
\newpage

\chapter{Experiment: Transverse oscillation of a string}
\section{Introduction}

\subsection{Goal of the experiment}
The goal of this experiment is to experimentally verify the stationary solutions of the wave equation. In order to do this, we are going to look for resonance frequencies of a string.
\subsection{Theory}
\subsection{Error calculation}

\section{Experiment setup and execution}
The Materials for this experiment are the following: 

\begin{itemize}
  \item A string and a clamping mechanism which allows adjusting and measuring the force applied to the string.
  \item Two clamps with connectors for standard electic wires.
  \item A wave-generator
  \item An AC amplifier
  \item A multimeter
  \item A magnet
  \item 6 wires
\end{itemize}
The string is fitted in the clamping mechanism and the clamps are fixed on either side of the fixed string. The magnet is then fitted underneath the string, allowing it to be moved along the string. Next, the electric equipment is installed by connecting the outputs of the wave generator parallel to both the inputs of the amplifier and the multimeter. The clamps are then connected to the outputs of the amplifier.
To avoid putting too much strain on the amplifier, we set the output voltage to just shy of $2\unit{V}$.

Using the regulator on the wave-generator, we now proceed to searching the spectrum for resonances, using the expected theoretical values as reference, listening and looking closely at the string.

\section{Measurements and Analysis}

\subsection[Frequency]{Frequency $\bm{f}$}

\begin{table}[H]
	\center
	\begin{tabular}{|c|c|cccccc|}
	\cline{2-8}
	 \multicolumn{1}{c|}{}& $n=$ & 1 & 2 & 3 & 4 & 5 & 6\\  \hline
	\multirow{2}{*}{$l=1\unit{m}$} & $K_1=14.7\unit{N}$ & 63.8 & 125.1 & 186.9 & 248.4 & 311.0 & 371.6\\
	& $K_2=29.4\unit{N}$ & 87.23 & 172.0 & 258.5 & 344.0 & 430.4 & 514.6\\
	\hline
	\end{tabular}
	\caption{String frequency $f$ in Hertz [Hz] at highest oscillation amplitude under distinct tensile forces $F_1, F_2$ and in oscillation modes $n=1,...,6$ with string length $l=1\unit{m}$}
\end{table}

\subsection[Mass per length]{Mass per length $\bm{\mu}$}

\begin{equation}
v=\sqrt{\frac{K}{\mu}}=\lambda_n f_n \Rightarrow \mu = \frac{K}{\lambda_n^2 f_n^2} 
\end{equation}

\begin{table}[H]
	\center
	\begin{tabular}{|c|c|cccccc|}
	\cline{2-8}
	 \multicolumn{1}{c|}{}& $n=$ & 1 & 2 & 3 & 4 & 5 & 6\\  \hline
	\multirow{2}{*}{$l=1\unit{m}$} & $K_1$ & 9.029e-4 & 9.393e-4 & 9.469e-4 & 9.530e-4 & 9.499e-4 & 9.581e-4\\
	& $K_2$ & 9.660e-4 & 9.938e-4 & 9.899e-4 & 9.938e-4 & 9.919e-4 & 9.992e-4\\
	\hline
	\end{tabular}
	\caption{Calculated mass per length $\mu$ [$\frac{\unit{kg}}{\unit{m}}$]}
\end{table}

\begin{table}[H]
\center
\begin{tabular}{|c|ccc|}
\cline{2-4}
\multicolumn{1}{c|}{}& $\bar{\mu}$ & $s_{\mu}$ & $s_{\bar{\mu}}$\\ \hline
$F_1$ & 9.417e-4 & 2.002e-5 & 8.954e-6 \\ \hline
$F_2$ & 9.891e-4 & 1.175e-5 & 5.255e-6\\ \hline
\end{tabular}
\caption{Mean $\bar{\mu}$, standard deviation $s_{\mu}$ and standard error of mean $s_{\bar{\mu}}$} of mass per length $\mu$ in [$\unit{\frac{kg}{m}}$]
\end{table}

\subsection[Transervse propagation speed]{Transverse propagation speed $\bm{v}$}

\begin{equation}
v=\lambda_n f_n
\end{equation}

\begin{table}[H]
	\center
	\begin{tabular}{|c|c|cccccc|}
	\cline{2-8}
	 \multicolumn{1}{c|}{}& $n=$ & 1 & 2 & 3 & 4 & 5 & 6\\  \hline
	\multirow{2}{*}{$l=1\unit{m}$} & $K_1$ & 127.6 & 125.1 & 124.6 & 124.2 & 124.4 & 123.867\\
	& $K_2$ & 174.46 & 172.0 & 172.333 & 172.0 & 172.16 & 171.533\\
	\hline
	\end{tabular}
	\caption{Calculated transverse propagation speed $v$ in [$\unit{\frac{m}{s}}]$}
\end{table}

\begin{table}[H]
\center
\begin{tabular}{|c|ccc|}
\cline{2-4}
\multicolumn{1}{c|}{}& $\bar{v}$ & $s_{v}$ & $s_{\bar{v}}$\\ \hline
$K_1$ & 124.961 & 1.357 & 0.607 \\ \hline
$K_2$ & 172.414 & 1.037 & 0.464\\ \hline
\end{tabular}
\caption{Mean $\bar{v}$, standard deviation $s_{v}$ and standard error of mean $s_{\bar{v}}$} of transverse propagation speed $v$ in [$\unit{\frac{m}{s}}$]
\end{table}

\section{Discussion}

\begin{thebibliography}{9}

\bibitem{physcript13}
  Peter Wurz,
  \emph{Anleitung zum Physikpraktikum}
  FS2013

\end{thebibliography}

\end{document}
